\documentclass[11pt]{article}       % set main text size
\usepackage[letterpaper,                
top=0.5in,                          
bottom=0.5in,                       
left=0.5in,                         
right=0.5in]{geometry}              

%=========================================
% FONT, COLOR, AND STYLE IMPROVEMENTS
%=========================================
\usepackage{mathpazo}       % Elegant Palatino serif font for body text
\usepackage[scaled]{mathpazo}     % Helvetica for section titles / name
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{xcolor}            % Color for text and titles
\colorlet{bodygray}{gray!20!black}     % Subtle gray for main text
\colorlet{titleblack}{black}           % Deep black for section headers
\colorlet{namegray}{gray!10!black}     % Lighter gray for contact info

\usepackage{enumitem}               
\usepackage[hidelinks]{hyperref}    
\usepackage{titlesec}               
\raggedright                        
\pagestyle{empty}                   

% ensure PDF output will be all-Unicode and machine-readable
\input{glyphtounicode}
\pdfgentounicode=1

%=========================================
% SECTION HEADINGS
%=========================================
\titleformat{\section}
  {\color{titleblack}\normalfont\Large\bfseries\scshape}
  {}{0pt}{}
  [\vspace{1pt}\titlerule\vspace{-6pt}]

%=========================================
% BULLET STYLING
%=========================================
\renewcommand\labelitemi{$\vcenter{\hbox{$\circ$}}$}
\setlist[itemize]{itemsep=1pt, leftmargin=14pt, topsep=5pt}

%=========================================
% GLOBAL TEXT COLOR
%=========================================
\color{bodygray}

%=========================================
% RESUME BEGINS HERE
%=========================================
\begin{document}
%==============================
% NAME & CONTACT
%==============================
\centerline{\Huge Emily R. McColville}

\vspace{5pt}

\centerline{\href{mailto:contact@mccolville.com}{contact@mccolville.com} \;|\; Ottawa, ON \;|\; 
\href{https://linkedin.com/in/emilymcvl}{linkedin.com/in/emilymcvl} \;|\; 
\href{https://github.com/emilymcvl}{github.com/emilymcvl}}

\vspace{-10pt}

%==============================
% SKILLS
%==============================
\section*{Skills}
\textbf{Research \& Analysis:} AI Model Development, RNA-Seq, Statistical Modeling, Scientific Writing \\
\textbf{Technical:} Python, R, TensorFlow, PyTorch, DeepLabCut, OpenCV, NumPy, Pandas, Scikit-Learn, AWS, Git \\
\textbf{Communication:} Public Speaking, Science Communication, Academic Writing, Bilingual (Korean, Intermediate)

\vspace{-4pt}

%==============================
% EDUCATION
%==============================
\section*{Education}
\textbf{Carleton University} -- PhD in Biology (AI and Bioinformatics) \hfill Expected 2025 \\
\textbf{Carleton University} -- B.Sc. (Honours) in Biology \hfill 2018 -- 2022

\vspace{-4pt}



%==============================
% PROJECTS
%==============================
\section*{Projects}

\textbf{Blooop – Digital Research Notebook} \hfill Present \\
\vspace{-6pt}
\begin{itemize}
  \item Developing a cross-platform digital notebook for researchers using Flutter/Dart with Riverpod and Hive/SQLite architecture.
  \item Designing a universal file reader, hybrid text editor and whiteboard interface supporting handwriting, dynamic text, and scientific calculators (e.g., media prep, molarity, C1V1).
\end{itemize}

\textbf{AstroLedger – Pattern-Discovery and Trend Mapping System} \hfill May 2024 -- Present \\
\vspace{-6pt}
\begin{itemize}
  \item Designed a data visualization system correlating global events (e.g., geopolitical shifts, pandemics), financial indicators (e.g., S&P 500 trends, crypto volatility), and esoteric frameworks (e.g., Tzolk’in, Wu Xing, Kabbalah, Gematria, Hermetic astrology).
  \item Implemented analytics pipeline using Python and D3.js for time-series trend tracking and interactive dashboards.
\end{itemize}

\textbf{AI-Driven Insect Imaging Model} \hfill Sept 2023 -- A 2024 \\
\vspace{-6pt}
\begin{itemize}
  \item Built an AI-based imaging pipeline to automate measurement and tracking of edible crickets, enabling data-driven scalability in insect-farming R&D, supporting sustainable alternative farming
  \item Reduced manual measurement time by 80\% and enabled individual growth analytics
  \item Research supported by the National Research Council and Mitacs; presented internationally and received a conference award.
\end{itemize}





%==============================
% EMPLOYMENT
%==============================
\section*{Employment}

\textbf{Consulting Researcher, Aspire} \hfill Sept 2024 -- May 2025 \\
\vspace{-6pt}
\begin{itemize}
  \item Advised internal research teams on AI model development to enhance R\&D scalability and optimization for biological analysis. 
  \item Advised on hyperspectral imaging workflows to improve experimental throughput and quality control
  \item Delivered technical reports and strategic recommendations to streamline data processing pipelines and automation efficiency. 
\end{itemize}

\textbf{MITACS Industry Researcher, BugMars} \hfill Apr 2024 -- Dec 2024 \\
\vspace{-6pt}
\begin{itemize}
  \item Partnered with industry on AI-based imaging systems for insect research and automation under a \$30,000 Mitacs Accelerate Grant.
  \item Managed image pipelines and AWS data storage; labeled and annotated 10,000+ images for machine learning training datasets.
\end{itemize}

\textbf{Teaching Assistant, Carleton University} \hfill Sept 2021 -- Present \\
\vspace{-6pt}
\begin{itemize}
  \item Led tutorials and laboratory sessions in advanced and comparative anatomy for 100+ undergraduates.
  \item Provided detailed written feedback on 300+ lab reports per semester, improving academic performance
  \item Received Teaching Assistant Excellence Award (2024) for exceptional instructional mentorship.
\end{itemize}

\textbf{Contract Researcher, Carleton University} \hfill May 2022 -- Aug 2022 \\
\vspace{-6pt}
\begin{itemize}
  \item Conducted laboratory experiments on microplastic ingestion in insects to assess environmental impacts of biosolid treatments.
  \item Processed and analyzed large laboratory and spectroscopy datasets relevant to environmental policy development.
\end{itemize}

\textbf{Residence Fellow, Carleton University} \hfill Sept 2019 -- Apr 2020 \\
\vspace{-6pt}
\begin{itemize}
  \item Supervised 60+ residence students, providing academic, social, and crisis management support.
  \item Designed residence programming to promote inclusivity and community engagement.
\end{itemize}

%\begin{itemize}
  %\item Performed vendor reconciliations and completed year-end financial records with high accuracy.
  %\item Streamlined accounting processes and improved efficiency through organized data workflows.
%\end{itemize}

%\textbf{Retail Associate, Cycling Elements} \hfill May 2020 -- Aug 2021 \\
%\vspace{-6pt}
%\begin{itemize}
  %\item Managed retail operations with daily sales exceeding \$20K, coordinated customer service and appointments 
  %\item Maintained inventory and optimized retail workflow during peak summer seasons.
%\end{itemize}

\vspace{-4pt}

%==============================
% RESEARCH & PUBLICATIONS
%==============================
\section*{Research \& Publications}

\textbf{Life Science Beyond Earth: Exploring the Legal Landscape in Outer Space Exploration} \\
\textit{IAF Proceedings (2024); IISL Publication (2026),} \href{https://doi.org/10.52202/078384-0070}{DOI: 10.52202/078384-0070} \\[6pt]

\textbf{Crickets Under Pressure: AI and RNA-seq Insights into Insect Immunity and Resilience for Food Systems on Earth and Beyond} \\
\textit{PhD Dissertation in progress, Carleton University.} \\[6pt]

\textbf{Microplastics in the Digestive Tract of Gryllus pennsylvanicus Crickets in a Biosolid-Treated Agricultural Field} \\
\textit{Nature: Scientific Reports, 2025,} \href{https://doi.org/10.1038/s41598-025-06895-w}{DOI: 10.1038/s41598-025-06895-w} \\[6pt]

\textbf{The Disadvantage of Having a Big Mouth: The Relationship Between Insect Body Size and Microplastic Ingestion} \\
\textit{Environmental Science \& Technology, Accepted 2025,} \href{https://doi.org/10.1101/2025.01.16.633357}{DOI: 10.1101/2025.01.16.633357} \\[6pt]

\textbf{Diet Particle Size Influences Tropical House Cricket Life History} \\
\textit{Journal of Insects as Food and Feed, 2025,} \href{https://doi.org/10.1163/23524588-00001365}{DOI: 10.1163/23524588-00001365} \\[6pt]

\textbf{Applying Nutritional Ecology to Optimize Diets of Crickets Raised for Food and Feed} \\
\textit{Royal Society Open Science, 2024,} \href{https://doi.org/10.1098/rsos.241710}{DOI: 10.1098/rsos.241710} \\[6pt]

\textbf{Carbonodraco lundi gen. et sp. nov.: The Oldest Parareptile and New Insights into Early Reptile Radiation} \\
\textit{Royal Society Open Science, 2019,} \href{https://doi.org/10.1098/rsos.191191}{DOI: 10.1098/rsos.191191}

\vspace{-4pt}

%==============================
% AWARDS & SCHOLARSHIPS
%==============================
\section*{Awards \& Scholarships}

\textbf{Summit for Space Sustainability Travel Grant (New York)} \\
{\color{gray!60!black}\textit{Space Generation Advisory Council, Secure World Foundation, \& UK Space Agency}} – Awarded \$3,500 USD for video submission on space sustainability (2023). \\[6pt]

\textbf{Mitacs Innovation Grant (\$30,000 CAD)} \\
{\color{gray!60!black}\textit{Mitacs Canada}} – Supported AI-driven insect research for sustainability and automation (2023–2024). \\[6pt]

\textbf{Canadian Reduced Gravity Experimental Design Competition (Longueuil)} \\
{\color{gray!60!black}\textit{National Research Council Canada \& Canadian Space Agency}} – Awarded microgravity flight campaign; recognized for novelty and excellence in space-biology research proposal and successful flight readiness completion (2024). \\[6pt]

\textbf{Best Poster – Insects to Feed the World (Singapore)} \\
{\color{gray!60!black}\textit{Insects to Feed the World Conference Committee}} – Third place for AI-model research presentation (2024). \\[6pt]

\textbf{Best Talk – Insect Biotechnology Conference (Niagara)} \\
{\color{gray!60!black}\textit{Insect Biotechnology Conference Committee}} – Third place for AI model development presentation (2022). \\[6pt]

\textbf{Teaching Assistant Excellence Award} \\
{\color{gray!60!black}\textit{Carleton University, Department of Biology}} – Recognized for outstanding instructional performance and mentorship (2024). \\[6pt]

\textbf{Academic All-Canadian} \\
{\color{gray!60!black}\textit{U Sports \& Carleton Athletics}} – Maintained 80\%+ GPA while competing as a varsity athlete (2021).


%==============================
% ACTIVITIES & INTERESTS
%==============================
\section*{Activities \& Interests}

\textbf{Varsity Rower} – Competed in LW1, LW2, and 8+ events; balanced 15+ hrs/week of training with full-time studies; recognized as Academic All-Canadian. \\[4pt]

\textbf{Judo Athlete \& Coach} – Trains 10 hrs/week and coaches youth 1.5 hrs/week at the RA Judo Club, emphasizing discipline and mentorship. \\[4pt]

\textbf{Canon Canada Futures Cohort} – Selected participant focusing on science communication and wildlife photography. \\[4pt]

\textbf{Korean Language Study} – Continuing study of Korean grammar, reading, and conversation for academic and personal fluency. \\[4pt]


\textbf{Let’s Talk Science Volunteer} – Designed and delivered educational modules on astro-agriculture to Ottawa-area schools, promoting youth engagement in sustainability and STEM.
\end{itemize}


\end{document}